Merging merges, more or less

### 2015-04-04 2015mergingmerges/section/03-Merging.tex
remove vertical special case

\subsection{Producer-consumer}
The general case above is sufficient, but in some cases can generate larger machines than necessary.
Talk about special case for producer-consumers.

\begin{code}
data Which = LeftExec | RightExec

mergeV :: Machine l1 -> Machine l2
       -> Machine (l1, l2, Which)
\end{code}

@@

For the special case of vertical fusion, we require there be one output used as the other machine's sole input, and no other sharing.
Both machines may have multiple outputs, and the producer may have multiple inputs, but the consumer can only have one input.

\begin{tabbing}
MMMMMMM \= MM \= MM \= \kill
$@vertical@~a~b$
\> $:=$
\> $\exists n.$
\> $(n \in \outputs{a} \wedge \sgl{n} = \inputs{b})$
\\
\>
\> $~\vee$
\> $(n \in \outputs{b} \wedge \sgl{n} = \inputs{a})$
\end{tabbing}

\subsubsection{General preservation}
The result of merging two machines should maintain the pull invariants (\S~\ref{s:Machines:Invariants}), provided that the input machines also maintain their invariants.

@@

\subsubsection{Vertical preservation}

\begin{tabbing}
MMMMMMM \= MM \= MM \= \kill
$\forall a~b.$
\>
\> $a~@ok@~\wedge~b~@ok@$
\\
\> $\wedge$
\> $@acyclic@~a~b$
\\
\> $\wedge$
\> $@vertical@~a~b$
\\
\> $\wedge$
\> $@distinct@~a~b$
\\
\> $\implies$
\> $\forall c \in (@mergeV@~a~b).\ c~@ok@$
\end{tabbing}

\subsubsection{Vertical progress}

\begin{tabbing}
MMMMMMM \= MM \= MM \= \kill
$\forall a~b.$
\>
\> $a~@ok@~\wedge~b~@ok@$
\\
\> $\wedge$
\> $@acyclic@~a~b$
\\
\> $\wedge$
\> $@vertical@~a~b$
\\
\> $\wedge$
\> $@distinct@~a~b$
\\
\> $\implies$
\> $\exists c.\ c \in @mergeV@~a~b$
\end{tabbing}

>>>>

@@

\subsubsection{Preservation}
The result of merging two machines should maintain the pull invariants (\S~\ref{s:Machines:Invariants}), provided that the input machines also maintain their invariants.

@@
